---
title: <h1>About me</h1>
---

<div class = "row">

<div class = "col-md-5">
*Zootecnista*    
[Universidad Nacional de Colombia sede Medellín](http://medellin.unal.edu.co/)   
email: edavidja@unal.edu.co  
<br>
_______________________________________  
*Analista de Datos*   
[Grupo Éxito](https://www.grupoexito.com.co/es)  
email: edavidj@grupo-exito.com
</div>

<div class = "col-md-4">
```{r fig.asp=0.35, echo=FALSE, fig.align='left'}
library(png)
library(grid)
img <- readPNG("images/logo_unal.png")
grid.raster(img)
```
<br>
<br>
```{r fig.asp=0.35, echo=FALSE, fig.align='left'}
library(png)
library(grid)
img <- readPNG("images/logo-exito.png")
grid.raster(img)
```
</div>
</div>

## Education

  - [Zootecnia - Universidad Nacional de Colombia sede Medellín](https://cienciasagrarias.medellin.unal.edu.co/index.php/zootecnia), 2015
  - [Especialización en estadística - Universidad Nacional de Colombia sede Medellín](http://ciencias.medellin.unal.edu.co/escuelas/estadistica/component/progracad/?snies=134), 2016.  
  - [Maestría en Inteligencia Analítica de Datos - Universidad de los Andes](https://industrial.uniandes.edu.co/es/programa-academico/maestria-en-inteligencia-analitica-de-datos-MIAD), *en curso*.  

## Teaching

  - 2021
    - Statistics - [University of Antioquia](http://www.udea.edu.co/wps/portal/udea/web/inicio/!ut/p/z1/hY7LDoIwEEW_hQVbOiCY6q5BXCAKJhixGwOmFkyhpCD8vo0aExMfs5u5554MoihDtMmHiud9JZtc6P1Ap0c88x2buBBhwEsg2zQK3N0aIPbQ_h9AdQxfhoDu0zvyMsDK9rQhSDZp7CeL0HkCPxwholzI4vEuaYoJ5ogqdmaKKeuq9Lns-7abm2DCOI4Wl5ILZp1kbcKnSim7HmXvJGrrDC6eGCJiGDfCwP1f/dz/d5/L2dBISEvZ0FBIS9nQSEh/)
    - R-Project in Animal Experimentation - [University of Antioquia](http://www.udea.edu.co/wps/portal/udea/web/inicio/!ut/p/z1/hY7LDoIwEEW_hQVbOiCY6q5BXCAKJhixGwOmFkyhpCD8vo0aExMfs5u5554MoihDtMmHiud9JZtc6P1Ap0c88x2buBBhwEsg2zQK3N0aIPbQ_h9AdQxfhoDu0zvyMsDK9rQhSDZp7CeL0HkCPxwholzI4vEuaYoJ5ogqdmaKKeuq9Lns-7abm2DCOI4Wl5ILZp1kbcKnSim7HmXvJGrrDC6eGCJiGDfCwP1f/dz/d5/L2dBISEvZ0FBIS9nQSEh/)
  - 2020
      - R-Project in Animal Experimentation - [University of Antioquia](http://www.udea.edu.co/wps/portal/udea/web/inicio/!ut/p/z1/hY7LDoIwEEW_hQVbOiCY6q5BXCAKJhixGwOmFkyhpCD8vo0aExMfs5u5554MoihDtMmHiud9JZtc6P1Ap0c88x2buBBhwEsg2zQK3N0aIPbQ_h9AdQxfhoDu0zvyMsDK9rQhSDZp7CeL0HkCPxwholzI4vEuaYoJ5ogqdmaKKeuq9Lns-7abm2DCOI4Wl5ILZp1kbcKnSim7HmXvJGrrDC6eGCJiGDfCwP1f/dz/d5/L2dBISEvZ0FBIS9nQSEh/)
  - 2019
      - Introduction to data analysis with R - Level 1 - [National University - Medellín, Colombia](https://medellin.unal.edu.co/)   
  - 2018
      - Biostatistics 1 - [National University - Medellín, Colombia](https://medellin.unal.edu.co/)   
      - Introduction to data analysis with R - Level 1 - [National University - Medellín, Colombia](https://medellin.unal.edu.co/)
      - Introduction to data analysis with R - Level 2 - [National University - Medellín, Colombia](https://medellin.unal.edu.co/)
        

## Experience  

  - Statistical consulting
      - Analysis of data of zootechnical interest in companies of the agricultural sector in Colombia.
      - Statistical analysis of microbiological tests on sanitary quality of meat.
      - Statistical application to parameters of animal welfare in horses.
  - Participation in planning and formulation of research projects.
  - Machine Learning uses in agriculture. Pathology detection in cows, satellite image analysis and biomusicology.  
  - Design and statistical analysis of experiments (agronomic experimentation, data collection, use of probabilistic models)
  - Software for data analysis
      - [R](https://cran.r-project.org/)
      - [Python](https://www.python.org/)
      - [Julia](https://julialang.org/)
      - [TensorFlow](https://www.tensorflow.org/)
      - [Keras](https://keras.io/)
      - [H2o](https://www.h2o.ai/)
      - Integrated development environments (IDEs)
          - [RStudio](https://www.rstudio.com/)
          - [Jupyter](http://jupyter.org/)
          - [Colaboratory](https://colab.research.google.com/notebooks/welcome.ipynb)